\documentclass[11pt, a4paper]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage[left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{fontawesome}


% --- Color and link configuration ---
\definecolor{linkcolor}{rgb}{0.0, 0.0, 0.5}
\hypersetup{
    colorlinks=false,
    hidelinks
}


% --- Section title configuration ---
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}



\newcommand{\cventry}[4]{
    \vspace{0.1cm}
    \noindent \textbf{#1} \hfill #2 \\
    \noindent \textit{#3} \hfill \textit{#4} \par
    \vspace{0.05cm}
}


\setlist[itemize]{label=\textbullet}

\begin{document}
\pagestyle{empty}

% ================= HEADER =================


\begin{center}
    {\Huge \textbf{Marcel ASSIE}} \\[0.2cm]
    {\Large \textsc{Geomatics Engineer}} \\[0.3cm]
    \footnotesize
    \faMobile~+33 7 68 06 25 78
    ~$|$~
    \faEnvelope~\href{mailto:marcelassie2k@gmail.com}{marcelassie2k@gmail.com}
    ~$|$~
    \faLinkedinSquare~\href{https://www.linkedin.com/in/marcel-assie/}{LinkedIn}
    ~$|$~
    \faGithub~\href{https://github.com/MarcelAssie/}{GitHub}
    ~$|$~
    \faGlobe~\href{https://marcel-assie.dev}{Portfolio}
    ~$|$~
    \faMapMarker~Champs-sur-Marne (77)
\end{center}

\vspace{0.3cm}
\noindent Geomatics engineering student specializing in spatial data science, passionate about the Geo-Data ecosystem and geospatial technologies. Seeking a \textbf{permanent full-time position} to leverage my skills in \textbf{geospatial software development}, \textbf{data pipeline automation}, and \textbf{spatial analysis}, serving high-impact projects that transform complex territorial data into effective decision-making tools.

% ================= EDUCATION =================
\section*{Education}

\cventry{École Nationale des Sciences Géographiques (Geodata Paris)}{Champs-sur-Marne, France}{Geomatics Engineering Degree \textbullet\ Spatial Data Science Specialization}{Sept. 2023 -- Sept. 2026}
\cventry{Institut National Polytechnique Félix Houphouët-Boigny}{Yamoussoukro, Ivory Coast}{Bachelor's Degree in Surveying}{Oct. 2019 -- Jul. 2022}
\cventry{Lycée Scientifique de Yamoussoukro}{Yamoussoukro, Ivory Coast}{French Baccalauréat (Scientific Stream)}{Sept. 2016 -- Jul. 2019}

% ================= PROFESSIONAL EXPERIENCE =================
\section*{Professional Experience}

\cventry{ISOGEO}{Paris, France}{GIS Developer -- Apprenticeship}{Sept. 2025 -- Sept. 2026}
\begin{itemize}[leftmargin=0.5cm, nosep]
    \item Led the technological overhaul of "Scan Isogeo" by replacing the FME ETL with new automated processing pipelines.
    \item Manipulated and processed a wide variety of geographic data formats (vector, raster, databases) using GDAL and SQL.
    \item Explored and implemented AI models to automatically extract and enrich semantic metadata.
    \item Drafted functional and technical specifications, and contributed to project management within an Agile team.
\end{itemize}

\cventry{ORYJIN}{Lille, France}{Geospatial Data Scientist -- Internship}{Apr. -- Aug. 2025}
\begin{itemize}[leftmargin=0.5cm, nosep]
    \item Researched, audited, and integrated various geospatial and socio-demographic data sources (INSEE, IGN) into the open-source H3 global grid system.
    \item Developed ETL pipelines and implemented statistical algorithms to calculate geographic aggregates (Python, Snowflake, SQL).
    \item Extracted spatial information (housing areas, infrastructure) from satellite imagery using Computer Vision AI models.
    \item Automated data visualization via generative AI: created descriptive models and prompt workflows to generate realistic images describing territories.
\end{itemize}

\cventry{IGN (National Institute of Geographic and Forest Information)}{Forcalquier, France}{Geomatics Engineer -- Internship}{May -- Jul. 2024}
\begin{itemize}[leftmargin=0.5cm, nosep]
    \item Conducted applied mini-projects in surveying, photogrammetry, metrology (bridge monitoring), remote sensing, and geodesy, including methodological formalization and uncertainty analysis.
    \item Designed an automated workflow for mapping traffic restrictions (Alpes-de-Haute-Provence):
    \begin{itemize}[leftmargin=0.5cm, nosep]
        \item Structured and cleaned multi-source datasets.
        \item Modeled geospatial processes (QGIS Model Builder).
        \item Developed quality control and data validation algorithms.
    \end{itemize}
\end{itemize}

% ================= SKILLS =================
\section*{Skills}
\noindent \textbf{Programming Languages:} Python, SQL, JavaScript, HTML/CSS, R, Cypher \\
\textbf{Technologies \& Frameworks:} Docker, GitHub, PostgreSQL/PostGIS, Django, Flask, Vue.js, React Native, Neo4j \\
\textbf{Libraries:} GDAL, Proj, GeoPandas, ArcPy, PyQGIS, Shapely, Leaflet.js \\
\textbf{GIS Software:} QGIS, ArcGIS Pro, FME, GeoServer, AutoCAD \\
\textbf{Soft Skills:} High adaptability, Rigor, Critical and analytical thinking, Proactive

% ================= PROJECTS =================
\section*{Projects}

\begin{itemize}[leftmargin=0.5cm, nosep]
    \item \textbf{Contextual Data Extraction (SDGs):}
    \begin{itemize}[leftmargin=0.5cm, nosep]
        \item Developed an advanced extraction method based on Large Language Models (LLMs) and structured it into knowledge graphs to analyze relationships between Sustainable Development Goals (PyTorch, Transformers, NLP, LLMs, Neo4j).
    \end{itemize}
    \vspace{0.2cm}
    \item \textbf{Mobile Navigation App (French National Gendarmerie):}
    \begin{itemize}[leftmargin=0.5cm, nosep]
        \item Developed a Waze-inspired application specifically tailored for public security missions (React Native, Flask).
    \end{itemize}
    \vspace{0.2cm}
    \item \textbf{Spatial Statistics Study (Île-de-France):}
    \begin{itemize}[leftmargin=0.5cm, nosep]
        \item Modeled the impact of transport network changes on commuting modal shifts through a spatio-temporal panel approach and prospective scenario simulation (Scikit-Learn, Seaborn, SciPy, Proj, GeoPandas).
    \end{itemize}
    \vspace{0.2cm}
    \item \textbf{KlassIvoire SaaS Platform:}
    \begin{itemize}[leftmargin=0.5cm, nosep]
        \item Contributed to the development of a digital school monitoring platform, integrating AI tools for performance analysis.
        \item Technologies: Django, SQL, PostgreSQL, Docker, Cloudflare R2, Redis, Gemini API.
    \end{itemize}
    \vspace{0.2cm}
    \item \textbf{Educational Institution Analysis Platform:}
    \begin{itemize}[leftmargin=0.5cm, nosep]
        \item Designed an intelligent geographic monitoring platform to leverage spatial data for decision-making.
        \item Technologies: Django, PostgreSQL/PostGIS, Leaflet.js.
    \end{itemize}
\end{itemize}


% ================= EXTRACURRICULAR =================
\section*{Extracurricular Activities \& Volunteering}

\cventry{Private Tutor}{Île-de-France}{In-home Tutoring -- Mathematics and Physics}{Since Oct. 2023}
\noindent Provided tailored pedagogy and methodology, highly attentive to students' needs.

\cventry{VERTIGEO -- ENSG Geomatics Junior Enterprise}{Champs-sur-Marne}{General Secretary}{Feb. 2024 -- Mar. 2025}
\noindent Drafted meeting minutes, managed archives and administrative partnerships, and organized meetings.

\cventry{Épicerie Solidaire Campésienne (Solidarity Grocery)}{Champs-sur-Marne}{Volunteer}{Feb. 2024}
\noindent Collected food and hygiene products at a Carrefour store. Promoted community exchange and open-mindedness.

% ================= LANGUAGES AND INTERESTS =================
\section*{Languages \& Interests}
\noindent \textbf{Languages:} French (Native), English (Professional Working Proficiency - TOEIC B2) \\[0.1cm]
\textbf{Interests:} Artificial Intelligence, Tech Watch, Soccer, Acrobatic Gymnastics, Board Games

\end{document}